### 2023-03-05 main/chapter_2ljets.tex
postit p166

My extrapolation scheme is fairly arbitrary, and is performed as follows.
Each benchmark point $i$ has a location in the parameter plane $\vec y_i$, and
for a given source of uncertainty $j$ its relative variation has been evaluated
as $r_{ij}$.
To extrapolate these variations across each parameter plane to another signal
model at $\vec x$, we use an exponentially weighted combination
\begin{equation}
\label{eqn:2ljets_signal_extrap}
r_j(\vec x) = \frac{
\sum_i r_{ij} e^{-d(\vec x, \vec y_i)}
}{
\sum_i e^{-d(\vec x, \vec y_i)}
}
\end{equation}
in which $d(\vec x, \vec y)$ is a distance function chosen to encode some
physical understanding into the extrapolation,
and the sum is over all benchmark points.

Parent mass $m(\chargino_1, \neutralino_2) = m_a$
and mass splitting $m_a - m_b$ are the most
characteristic features in C1N2.
From some experimentation, I found that a Manhattan distance in those features
extrapolated nicely.
Being a linear sum, the exponentiated Manhattan distance beneficially
separating into a product of terms, so contours of constant $r_j(\vec x)$ are
segmented into straight lines that relate to the chosen coordinates.
Alternatives, such as the Euclidean distance, produced curved contours that did
not align as well with my intuitions.
Since the mass distance is dimensionful, it needs to be scaled to a reference
value, which I chose as $100\,\eV[G]$; therefore
\begin{equation}
d_\mathrm{C1N2}(\vec x, \vec y) =
\frac{1}{100\,\eV[G]}
\big(
|m_a^{\vec x} - m_b^{\vec y}|
+
|(m_a^{\vec x} - m_b^{\vec x}) - (m_a^{\vec y} - m_b^{\vec y})|
\big)
.
\end{equation}
To put the Higgs branching fraction $B$ on a similar scale to the parent mass
for GMSB models, its distance measure has a separate scale factor;
\begin{equation}
d_\mathrm{GMSB}(\vec x, \vec y) =
\frac{1}{100\,\eV[G]}
|m_a^{\vec x} - m_b^{\vec y}|
+
5
|B^{\vec x} - B^{\vec y}|
.
\end{equation}
Some example extrapolations according to these rules are displayed in
Figure~\ref{fig:2ljets_signal_sys_extrap}.
This figure illustrates the common theme that our theory variations are small
if and only if signal yields are large enough for good statical precision.

>>>>

Most extrapolation schemes are fairly arbitrary, and our choice here is taken
for some heuristically attractive properties to be explained here.
Each benchmark point $i$ has a location in the parameter plane $\vec y_i$, and
for a given source of uncertainty $j$ its relative variation has been evaluated
as $r_{ij}$.
To extrapolate these variations across each parameter plane to another signal
model at $\vec x$, we use an exponentially weighted combination
\begin{equation}
\label{eqn:2ljets_signal_extrap}
r_j(\vec x) = \frac{
\sum_i r_{ij} e^{-d(\vec x, \vec y_i)}
}{
\sum_i e^{-d(\vec x, \vec y_i)}
}
,
\end{equation}
in which $d(\vec x, \vec y)$ is a distance function chosen to encode some
physical understanding into the extrapolation, and the sum is over all
benchmark points.
One benefit of this extrapolation scheme is that its results $r_j(\vec x)$
are bounded by range of the observed points $r_{ij}$;
alternatives, such as Radial Basis
Functions~\cite{2020SciPy-NMeth,fasshauer2007meshfree}, can extrapolate without
bound to large or small (negative) outputs, to extreme outputs, which do not
seem physically justified in this case.

This formulation of extrapolation as a weighted mixture has some freedom in
which to assign the distance function $d(\vec x, \vec y)$, and within that
freedom we can make choices that encode some physical understanding.
In the case of our C1N2 model, two characteristic features are the
parent mass $m(\chargino_1, \neutralino_2) = m_a$
and the mass splitting $m_a - m_b$, and we want an extrapolation scheme which
aligns changes in these variables with changes in the extrapolated value.
From some experimentation, I found that a Manhattan distance in these features
implements such attractive extrapolation:
being a linear sum, the exponentiated Manhattan distance beneficially
separates into a product of terms, so contours of constant $r_j(\vec x)$ are
segmented into straight lines that relate to the chosen coordinates.
Alternatives, such as the Euclidean distance, produced curved contours that did
not align as well with the $m_a$ and $m_a - m_b$ directions.
Since the mass distance is dimensionful, it must be scaled to a reference
value, which I chose as $100\,\eV[G]$; therefore
\begin{equation}
d_\mathrm{C1N2}(\vec x, \vec y) =
\frac{1}{100\,\eV[G]}
\big(
|m_a^{\vec x} - m_b^{\vec y}|
+
|(m_a^{\vec x} - m_b^{\vec x}) - (m_a^{\vec y} - m_b^{\vec y})|
\big)
.
\end{equation}
To put the Higgs branching fraction $B$ on a similar scale to the parent mass
for GMSB models, its distance measure has a separate scale factor;
\begin{equation}
d_\mathrm{GMSB}(\vec x, \vec y) =
\frac{1}{100\,\eV[G]}
|m_a^{\vec x} - m_b^{\vec y}|
+
5
|B^{\vec x} - B^{\vec y}|
.
\end{equation}
Some example extrapolations according to these rules are displayed in
Figure~\ref{fig:2ljets_signal_sys_extrap}.
This figure illustrates the common theme that our theory variations are small
if and only if signal yields are large enough for good statical precision.
